### 2021-09-03 README.Rmd
GH actions and dockerfile
dockerfile

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/benmarwick/systematicsinprehistory/master?urlpath=rstudio)

>>>>

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/benmarwick/systematicsinprehistory/master?urlpath=rstudio)  [![run on Docker](https://github.com/benmarwick/systematicsinprehistory/workflows/run-on-docker/badge.svg)](https://github.com/benmarwick/systematicsinprehistory/actions)
